### 2019-04-09 manuscript.tex
Update manuscript.tex

@@

- community level of effects -
\cite{ChegAske04}(community -based approach), \cite{BrowBeec13, Hayf05, KandShel19, PatrSing15, ShelWand11}
\cite{BellNova15}: "We find that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level."
- tipping point/threshold -

— secondary analysis/socio demograhpic —

@@

— Suggestions —
- empowering community, engaging community leaders and other strategies \citeBergDeni13b}
- MC vs. FGC.  Considering the acceptance of Alternative rights of passage \cite{GaluKama15} without criminalize the practice. (I'm not sure if I'm comfortable with this position, but it is an alternative.) vs. focused on empowerment, and campaigns to recruit change agents from within communities (to eradicate FGC) \cite{ShelHern13, Will18}

@@

— by nations and laws in those nations—
---- Kenya: legal background:  Kenya \cite{GKEN01}; \cite{UNIC13}; 
 vs. \cite{Chia14, Hayf05}, and [\url{http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya}]
---- Mali: ``The occurrence of FGM/C is also concentrated in certain West African countries where prevalence rates range from 72–96 percent: Burkina Faso, the Gambia, Guinea, and Mali. The populations of these countries share certain social and historical ties, which suggests that a strategy to eliminate FGM/C in one of these countries might be successful in others. FGM/C is practiced as part of the initiation into a secret society in Liberia and Sierra Leone. We should expect that the repercussions for mothers there who do not send their daughters to be initiated would be different than for mothers in nearby Mali or Guinea \cite{YodaWang13}

=================
% The findig “suggests that even with a sharp decrease in FGC prevalence, the bulk of FGC persistence would still come from household-level factors. This is in contrast to the tipping point and informational cascade models … , wherein the decision to abandon a social norm such as FGC should be entirely individual in places where the practice is highly pervasive.”  they found that “that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level”  \cite{BellNova15}; and to compare our results to \cite{BellNova15} because they agnostic about the three theories.

@@

\cfcmt{empirical norm:  enough others follow the norm-  community level of FGC \cite{Bicc10} normative norm:  enough others think we need to follow the norm -  FGC beliefs, decision on daughter's FGC status (already and future), \cite{Bicc10}}

“we find that some older women express an openness to reassessing norms and practices as they seek solutions to maintaining the physical well-being, moral integrity and cultural identity of girls in their families. Moreover, given the authority of older women over younger women, they also have power to negotiate change.\cite{ShelMore18}
% get info on legal situation of FGC in those countries

@@

%\cfcmt{a sentence on the national FGC policy of the 4 nations and gender law}
% "In 1997, the Ministry for the Promotion of Women in Mali created a National Committee Against Violence Towards Women that links all the international organizations active in preventing FGC in Mali" "In 2001, the Kenya legislature adopted a law banning FGC." "the founding father of the country (Kenyatta, 1962) explicitly linked FGC to nationalist pride."

@@

Egypt:  "Literate, better educated and employed women are more likely to oppose FGM" \cite{VanMeek15}
Sinegal: \cite{KandComb15}
West Africa:  \cite{SipsChen12} (law and current practices)
Theory:  
% gender symbol \cite{Youn04}
% gender autonomy \cite{Meye00}: 
%``Since autonomy-augmenting educational programs are typically developed by cultural initiates who rely on traditional modes of expression and appeal to traditional values, it is reasonable to surmise that autonomy is best extended by avoiding cultural alienation and by building on women's existing autonomy skills." 
% ``autonomy-augmenting programs regard women in cultures that practice female genital cutting as self-determining individuals. …they have some understanding of what matters to them and how best to proceed in light of their values and commitments before they participate in such programs. … women who are subject to female genital cutting are not without autonomy. But this understanding of autonomy entails neither endorsement of female genital cutting nor resignation to its persistence. Since cultures that practice female genital cutting may have selectively nurtured and stifled women's autonomy skills, and since these cultures may shield the issue of female genital cutting from exercise of autonomy skills, developing and coordinating women's autonomy skills and extending the range of application of these skills are key to augmenting their autonomy. ``
% convention or modernization theory?`` campaigns against FGC using educational, health, legal, and human rights–based approaches are at times ineffective and counterproductive when they frame the practice as a ``tradition" rooted in a ``primitive" and unchanging culture. We suggest that development interventions that do not address local contexts of FGC, including the complex politics and history of interventions designed to eradicate it, can in fact reify and reinscribe the practice as central to Maasai cultural identity." \cite{WintKoom09}

@@

% attitude change: "migrating to and living in Sweden facilitates a transition in attitudes regarding FGC" \cite{WahlJohn17}
\cite{UNFPA14, UNIC16}

@@

% attitudes change may be followed by behaviour change, but more slowly \cite{BoylMcMo02}
% Limitations:  without incorporating national factor in this study.

@@

% Based on our findings, are there any survey questions DHS should have included but did not?  Did our findings see something like group/community identity, womanhood \cite{Koom14}?
% \cite{Koom14}: `` an Aang Serian activist who had addressed a village meeting saying, `The world is changing and the Maasai must change with it or risk dying out.' They argued that these appeals to cultural survival were much more persuasive and meaningful to them than the `foreign' language of rights."

@@

% (Against common belief of a critical mass, an empirical model showed that FGC was not driven by a social norm based on coordination and there was no signal critical threshold for the practice because of various heterogeneity of the population \cite{EffeVogt15} \cfcmt{I don't know if I want to cite \cite{EffeVogt15}.  It doesn't cite some very important papers which had addressed the concerns/questions the paper suggested}).  Can heterogeneity explain the differences of beliefs in FGC benefits at individual level vs. at a community level?

@@

% Latikin 1995:  Norms o unsafe behaviours are not trivially changed trough information.
% Beliefs are susceptible social confirmation (Damon Centola)
% a chart to show changes of FGC prevalence from 2000 to the current surveys (Kenya 98, 03; Nigeria 99, 03; Mali 01, 06?  (see \cite{BoylCorl10}, table 1)

@@

%There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns: for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}…..Modernization theory proposed that, for example, education and \cite{BoylMcMo02, Youn02} can contribute to the reduction of FGC practice.

>>>>

\subsection{journals}\label{journals}
possible consideration:  The Lancet Global Health, Science, BMJ, Bulletin of WHO

@@

- community level of effects -
\cite{ChegAske04}(community -based approach), \cite{BrowBeec13, Hayf05, KandShel19, PatrSing15, ShelWand11}
\cite{BellNova15}: "We find that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level."
- tipping point/threshold -
\cfcmt{empirical norm:  enough others follow the norm-  community level of FGC \cite{Bicc10} normative norm:  enough others think we need to follow the norm -  FGC beliefs, decision on daughter's FGC status (already and future), \cite{Bicc10}}
— secondary analysis/socio demograhpic —

@@

— by nations and laws in those nations—

---- Kenya: legal background:  Kenya \cite{GKEN01}; \cite{UNIC13}; 
 vs. \cite{Chia14, Hayf05}, and [\url{http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya}]
---- Mali: ``The occurrence of FGM/C is also concentrated in certain West African countries where prevalence rates range from 72–96 percent: Burkina Faso, the Gambia, Guinea, and Mali. The populations of these countries share certain social and historical ties, which suggests that a strategy to eliminate FGM/C in one of these countries might be successful in others. FGM/C is practiced as part of the initiation into a secret society in Liberia and Sierra Leone. We should expect that the repercussions for mothers there who do not send their daughters to be initiated would be different than for mothers in nearby Mali or Guinea \cite{YodaWang13}

— Suggestions —
- empowering community, engaging community leaders and other strategies \citeBergDeni13b}
- MC vs. FGC.  Considering the acceptance of Alternative rights of passage \cite{GaluKama15} without criminalize the practice. (I'm not sure if I'm comfortable with this position, but it is an alternative.) vs. focused on empowerment, and campaigns to recruit change agents from within communities (to eradicate FGC) \cite{ShelHern13, Will18}
- modelling by plotting empirical data to study threshold/tipping point.
- redesign questions of fgc benefits in DHS
- inviting faced women migrated to western society to participate in fgc intervention campaign.  For example,  attitude change: "migrating to and living in Sweden facilitates a transition in attitudes regarding FGC" \cite{WahlJohn17}

— Limitation —
- No FGC types relating to our response varialbes

@@

% The findig “suggests that even with a sharp decrease in FGC prevalence, the bulk of FGC persistence would still come from household-level factors. This is in contrast to the tipping point and informational cascade models … , wherein the decision to abandon a social norm such as FGC should be entirely individual in places where the practice is highly pervasive.”  they found that “that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level”  \cite{BellNova15}; and to compare our results to \cite{BellNova15} because they agnostic about the three theories.

@@

“we find that some older women express an openness to reassessing norms and practices as they seek solutions to maintaining the physical well-being, moral integrity and cultural identity of girls in their families. Moreover, given the authority of older women over younger women, they also have power to negotiate change.\cite{ShelMore18}

@@

% "In 1997, the Ministry for the Promotion of Women in Mali created a National Committee Against Violence Towards Women that links all the international organizations active in preventing FGC in Mali" "In 2001, the Kenya legislature adopted a law banning FGC." "the founding father of the country (Kenyatta, 1962) explicitly linked FGC to nationalist pride."

@@

Egypt:  "Literate, better educated and employed women are more likely to oppose FGM" \cite{VanMeek15}
Sinegal: \cite{KandComb15}
West Africa:  \cite{SipsChen12} (law and current practices)
Theory:

% convention or modernization theory?`` campaigns against FGC using educational, health, legal, and human rights–based approaches are at times ineffective and counterproductive when they frame the practice as a ``tradition" rooted in a ``primitive" and unchanging culture. We suggest that development interventions that do not address local contexts of FGC, including the complex politics and history of interventions designed to eradicate it, can in fact reify and reinscribe the practice as central to Maasai cultural identity." \cite{WintKoom09}

@@

\cite{UNFPA14, UNIC16}

@@

% attitudes change may be followed by behaviour change, but more slowly \cite{BoylMcMo02}

@@

% Did our findings see something like group/community identity, womanhood \cite{Koom14}?
% \cite{Koom14}: `` an Aang Serian activist who had addressed a village meeting saying, `The world is changing and the Maasai must change with it or risk dying out.' They argued that these appeals to cultural survival were much more persuasive and meaningful to them than the `foreign' language of rights."

@@

% (Against common belief of a critical mass, an empirical model showed that FGC was not driven by a social norm based on coordination and there was no signal critical threshold for the practice because of various heterogeneity of the population \cite{EffeVogt15} \cfcmt{Can heterogeneity explain the differences of beliefs in FGC benefits at individual level vs. at a community level?}

@@

% a chart to show changes of FGC prevalence from 2000 to the current surveys (Kenya 98, 03; Nigeria 99, 03; Mali 01, 06?  (see \cite{BoylCorl10}, table 1)

@@
